Finite Property Convex Elicitation Paper

### 2019-01-25 cvx-fin.tex

For $3 \implies 1$, observe that for each level set $\theta \in \Theta$, there is a report $u \in \reals^d$ such that $\Gamma_u = \theta$.
Let $\R$ be the collection of such reports $u$ corresponding to each $\theta$.
The property $\gamma:p\mapsto \Gamma(p) \cap \R$ is then finite and embedded by $\Gamma$.
To see $\gamma$ is elicitable, consider that each level set of $\gamma$ is also a level set of $\Gamma$, and is therefore convex by the elicitability of $\Gamma$.
Since each level set is convex, we know $\gamma$ is elicitable.
\jessie{Cite?}
\end{proof}

@@

For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
Suppose $\Gamma$ is elicited by a polyhedral function and the link connecting $\gamma$ and $\Gamma$ was not separated.
Then either the embedded points are too close \jessie{...}.
If, for some $v \in B(\epsilon, u)$, we see $\psi(v) \neq \psi(u)$, then $\psi(v) \neq \psi(w)$ for some $w \neq u$.
\jessie{My brain is turning off and I didn't get to do nearly as much as I thought I was going to be able to tonight, but I'll iterate again in the morning.}
\end{proof}

@@

\begin{definition}
  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\leq 0$ such that $\gamma$ is $d$-embeddable.
\end{definition}

>>>>

For $3 \implies 1$, observe that for each level set $\theta \in \Theta$, there is a report $u \in \reals^d$ such that $\Gamma_u = \theta$.
Let $\R$ be the collection of such reports $u$ corresponding to each $\theta$.
The property $\gamma:p\mapsto \Gamma(p) \cap \R$ is then finite and embedded by $\Gamma$.
To see $\gamma$ is elicitable, consider that each level set of $\gamma$ is also a level set of $\Gamma$, and is therefore convex by the elicitability of $\Gamma$.
Since each level set is convex, we know $\gamma$ is elicitable.
\jessie{Cite Lambert 08 probably?}
\end{proof}

@@

For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
If the loss $L$ is polyhedral, then we can construct a $\psi$ so that the above holds.
If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.

\end{proof}

@@

\begin{definition}
  The \emph{embedding dimension} of a finite property $\gamma$, written $\elicembed(\gamma)$, is the minimum $d\leq 0$ \jessie{$d \geq 1?$} such that $\gamma$ is $d$-embeddable.
\end{definition}
